Models of lens candidates from Space Warps CFHTLS

### 2016-12-16 parts/stelmass.tex
figure changes
edits

The stellar masses of the lens galaxies are derived by comparison of
the photometric data with M/L estimates from population synthesis
models.  In principle, a detailed analysis of the spectral energy
distribution is needed to derive accurate stellar masses
\citep[e.g.][]{2009ApJS..185..253G,2011MNRAS.418.1587T}.
However, estimates to within 0.3\,dex in $\log($M$_s$/M$_\odot)$ can be
derived with a single colour, preferably tracing a rest-frame colour
similar to $U-V$ \citep[see fig.~1 of][]{2008MNRAS.383..857F}. This
paper presents a pilot study of the potential of SpaghettiLens to
constrain the physical properties of strong lenses. Therefore, we
further simplify the analysis by assuming a relationship between the
apparent total magnitude and stellar mass, at the redshift of the
lens. Note that for typical stellar population parameters, the
variation of this relation is at most 1\,dex. In this work, we make
use of the \citet{2003MNRAS.344.1000B} models to derive two functional
forms of the stellar mass with respect to SDSS-$i$ band
magnitudes. The models have solar metallicity, with a Chabrier
IMF, and assume two different age trends: a ``young'' model, with a
constant 500\,Myr age at all redshifts, and an ``old'' model where the
age is the oldest one possible at each redshift, adopting a
standard $\Lambda$CDM model with $H_0=70$\,km\,s$^{-1}$\,Mpc$^{-1}$
and $\Omega_m=0.3$. We take a geometric mean of the output from these
two models as the stellar mass of the lens. This rough estimate will
be improved in future versions by use of the available optical and NIR
magnitudes to derive more accurate constrains on the stellar
populations.

@@

\begin{figure*}
\includegraphics[width=\linewidth]{img/mlens_vs_mstel_one/mstel_vs_mtot_one}
\caption{}
\end{figure*}

>>>>

The stellar masses of the lens galaxies are derived by comparison of
the photometric data with M/L estimates from population synthesis
models.  In principle, a detailed analysis of the spectral energy
distribution is needed to derive accurate stellar masses
\citep[e.g.][]{2009ApJS..185..253G,2011MNRAS.418.1587T}.  However,
estimates to within 0.3\,dex in $\log($M$_s$/M$_\odot)$ can be derived
with a single colour, preferably tracing a rest-frame colour similar
to $U-V$ \citep[see fig.~1 of][]{2008MNRAS.383..857F}.

In this paper we further simplify the analysis by assuming a
relationship between the apparent total magnitude and stellar mass, at
the redshift of the lens.  For typical stellar population parameters,
the variation of this relation is at most 1\,dex.  A further possible
systematic error is contamination of the light of the lensing galaxy
by the lensed galaxy.  Reducing or eliminating the latter would
require detailed fitting of light distributions for each candidate,
which we have not yet attempted.  These caveats notwithstanding, it is
still interesting to compare the derived stellar mass with the lensing
mass.

We make use of the \citet{2003MNRAS.344.1000B} models to derive two
functional forms of the stellar mass with respect to SDSS-$i$ band
magnitudes. The models have solar metallicity, with a Chabrier IMF,
and assume two different age trends: a ``young'' model, with a
constant 500\,Myr age at all redshifts, and an ``old'' model where the
age is the oldest one possible at each redshift, adopting a standard
$\Lambda$CDM model with $H_0=70$\,km\,s$^{-1}$\,Mpc$^{-1}$ and
$\Omega_m=0.3$. We take a geometric mean of the output from these two
models as the stellar mass of the lens. This rough estimate will be
improved in future versions by use of the available optical and NIR
magnitudes to derive more accurate constrains on the stellar
populations.

@@
